The Impact of Education <br>

### 2014-12-03 Presentation/EdEntrePres.Rmd
Added table to map slide
Minor edits to pres

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#fff7bc', '#d95f0e']"
))

@@

## Slide with R Code and Output
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(stargazer)

@@

```{r, echo =FALSE, cache=FALSE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

@@

>>>>

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

# Duplicate D4 df
Dropped4 <- D4

# Drop iso2c in Dropped4
Dropped4$iso2c <- NULL

Table <- gvisTable(Dropped4, 
               options=list(width=230, height=300))

MT <- gvisMerge(Opp_map, Table, horizontal = TRUE)

@@

## Slide with R Code and Output
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

# Library stargazer
library(stargazer)

@@

```{r, echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

@@

## New
```{r, echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
